Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-04-09 main/doc/building_scope.tex
documentation

Chord computes the analysis scope (i.e., reachable classes and methods) of a given Java program
either if property \code{chord.build.scope} is set to \code{true} or if some other task (e.g.,
a program analysis specified via property \code{chord.run.analyses}) demands it by
calling static method \code{chord.program.Program.v()}.

>>>>

Chord computes the analysis scope (i.e., reachable classes and methods) of the given program
either if property \code{chord.build.scope} is set to \code{true} or if some other task (e.g.,
a program analysis specified via property \code{chord.run.analyses}) demands it by
calling method \code{chord.program.Program.v()}.
